\documentclass[10pt,oneside]{memoir}
\usepackage{layouts}[2001/04/29]
\makeglossary
\makeindex

\def\mychapterstyle{default}
\def\mypagestyle{headings}
\def\revision{}

%%% need more space for ToC page numbers
\setpnumwidth{2.55em}
\setrmarg{3.55em}

%%% need more space for ToC section numbers
\cftsetindents{part}{0em}{3em}
\cftsetindents{chapter}{0em}{3em}
\cftsetindents{section}{3em}{3em}
\cftsetindents{subsection}{4.5em}{3.9em}
\cftsetindents{subsubsection}{8.4em}{4.8em}
\cftsetindents{paragraph}{10.7em}{5.7em}
\cftsetindents{subparagraph}{12.7em}{6.7em}

%%% need more space for LoF numbers
\cftsetindents{figure}{0em}{3.0em}

%%% and do the same for the LoT
\cftsetindents{table}{0em}{3.0em}

%%% set up the page layout
\settrimmedsize{\stockheight}{\stockwidth}{*}	% Use entire page
\settrims{0pt}{0pt}

\setlrmarginsandblock{1.5in}{1.5in}{*}
\setulmarginsandblock{1.5in}{1.5in}{*}

\setmarginnotes{17pt}{51pt}{\onelineskip}
\setheadfoot{\onelineskip}{2\onelineskip}
\setheaderspaces{*}{2\onelineskip}{*}
\checkandfixthelayout

\usepackage{fancyvrb}			% Allow \verbatim et al. in footnotes
\usepackage{graphicx}			% To include graphics in pdf's (jpg, gif, png, etc)
\usepackage{booktabs}			% Better tables
\usepackage{tabulary}			% Support longer table cells
\usepackage[utf8]{inputenc}		% For UTF-8 support
\usepackage[T1]{fontenc}		% Use T1 font encoding for accented characters
\usepackage{xcolor}				% Allow for color (annotations)

%\geometry{landscape}			% Activate for rotated page geometry

%\usepackage[parfill]{parskip}	% Activate to begin paragraphs with an empty
								% line rather than an indent


\def\myauthor{Author}			% In case these were not included in metadata
\def\mytitle{Title}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\bibliocommand{}

\VerbatimFootnotes
\def\myauthor{Jenee Hughes}
\def\baseheaderlevel{1}
\def\format{complete}
\def\mytitle{ThesisDocumentsMelodyMatcher}


%
%	PDF Stuff
%

%\ifpdf							% Removed for XeLaTeX compatibility
%  \pdfoutput=1					% Removed for XeLaTeX compatibility
  \usepackage[
  	plainpages=false,
  	pdfpagelabels,
  	pdftitle={\mytitle},
  	pagebackref,
  	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}
  \usepackage{memhfixc}
%\fi							% Removed for XeLaTeX compatibility


%
% Title Information
%


\ifx\latexauthor\undefined
\else
	\def\myauthor{\latexauthor}
\fi

\ifx\subtitle\undefined
\else
	\addtodef{\mytitle}{}{ \\ \subtitle}
\fi

\ifx\affiliation\undefined
\else
	\addtodef{\myauthor}{}{ \\ \affiliation}
\fi

\ifx\address\undefined
\else
	\addtodef{\myauthor}{}{ \\ \address}
\fi

\ifx\phone\undefined
\else
	\addtodef{\myauthor}{}{ \\ \phone}
\fi

\ifx\email\undefined
\else
	\addtodef{\myauthor}{}{ \\ \email}
\fi

\ifx\web\undefined
	\else
		\addtodef{\myauthor}{}{ \\ \web}
\fi

\title{\mytitle}
\author{\myauthor}

\begin{document}

\chapterstyle{\mychapterstyle}
\pagestyle{\mypagestyle}

%
%		Front Matter
%

\frontmatter


% Title Page

\maketitle
\clearpage

% Copyright Page
\vspace*{\fill}

\setlength{\parindent}{0pt}

\ifx\mycopyright\undefined
\else
	\textcopyright{} \mycopyright
\fi

\revision

\begin{center}
\framebox{ \parbox[t]{1.5in}{\centering Formatted for \LaTeX  \\ 
 by MultiMarkdown}}
\end{center}

\setlength{\parindent}{1em}
\clearpage

% Table of Contents
\tableofcontents
%\listoffigures			% activate to include a List of Figures
%\listoftables			% activate to include a List of Tables


%
% Main Content
%


% Layout settings
\setlength{\parindent}{1em}

\mainmatter
Or, more simply:
Life would be ec-sta-sy
This musical emphasis matches the spoken emphasis of the phrase, so it is intelligible as a lyric. (Though ecstasy's first syllable doesn't start on the first part of beat three, it is still on the first part of beat three, and therefore still emphasized. Alternatively, since the first part of beat two didn't have a hard stop to it, the emphasis could have rolled over to the second part, ``ec'', which does have a hard stop.)
In contrast, take the second measure: the syllables ``You'', ``me'', and ``less'' are emphasized in the music. This leads to conflicting musical and spoken phrasing:
Musical Phrasing: You and me endlessly 
Spoken Phrasing: You and me endlessly
The singer is now singing the phrase, syllable by syllable, which they think of as syllable-note combinations:
YOU and ME end LESS lee
The singer, for his part, is doing what many singers are taught to do, to make it easier to sustain the singing of words that end with unsingable consonants: the unsingable consonant is displaced onto the front of the next word. In this case, the consonant ``d'' is not singable, so he displaces it onto the next syllable, when he can: ``and ME'' becomes ``an dME'', and ``end LESS'' becomes ``en dLESS''. So, the singer can effectively think of the sung phrase as:
YOU an dME en dLESS lee


This doesn't cause confusion for listeners, because they're used to hearing it. This does mean, however, that lyric placement does not provide an accurate barometer to a listener of where a word actually ends.
In addition, the singer is singing fudging his vowels, like singers are taught to do, so ``and'' and ``end'' sound almost indistinguishable. So, really, what listeners are hearing is this:
YOU en dME en dLESS lee


Now, the listener's brain has to take this syllabic gobbledy- gook, and parse it into something useful. They've currently got this mess to deal with (represented in SAMPA syllables):
ju En dmi En dl@s li
 They parse the first part just fine, because the emphases
you and me En dl@s li
But no one says endLESSly. People say ENDlessly. So, the listeners don't recognize it. They have to work with what they have. They already turned one ``En d'' into an ``and'', so they do it again:
you and me and l@s li
Now, they're just left with LESS lee. And that fits Leslie, a proper noun that fits in context and in emphasis placement. So, the final heard lyric is:
you and me and Les- lie
The misunderstanding can be traced back to improper emphasis placement. The songwriter probably didn't even think of that, and now he's stuck: a one-hit-wonder with a misunderstood song. We bet that in interview after interview, someone asks him who Leslie is. It's probably very frustrating --- especially since he could have just moved the word an eight note later, and it would have been understood perfectly.
That's the sort of situation this program is going to help avoid.
III. FUTURE WORK
We plan to continue developing and refining the methods through which Melody Matcher makes its determinations. Eventually, we plan to use this as an underlying framework for an interactive virtual environment where your surroundings are affected and created via musical and lyrical input. This should be completed in March 2012, with incremental updates discussed on www.melodymatcher.com.
IV. CONCLUSION
In this paper, we have discussed at a high level parts of the music-lingustic approach that Melody Matcher takes to measure the intelligibility of lyrics. We covered some of the major reasons that lyrics get misheard, along with a few examples. Melody Matcher's specific implementation details, while fully specified elsewhere, were outside the scope of this abstract, and we hope to cover them in a later paper.


%
% Back Matter
%

\backmatter
%\appendixpage

%	Bibliography
\bibliographystyle{\mybibliostyle}
\bibliocommand

%	Glossary
\printglossary


%	Index
\printindex

\end{document}
