\documentclass[10pt,oneside]{memoir}
\usepackage{layouts}[2001/04/29]
\makeglossary
\makeindex

\def\mychapterstyle{default}
\def\mypagestyle{headings}
\def\revision{}

%%% need more space for ToC page numbers
\setpnumwidth{2.55em}
\setrmarg{3.55em}

%%% need more space for ToC section numbers
\cftsetindents{part}{0em}{3em}
\cftsetindents{chapter}{0em}{3em}
\cftsetindents{section}{3em}{3em}
\cftsetindents{subsection}{4.5em}{3.9em}
\cftsetindents{subsubsection}{8.4em}{4.8em}
\cftsetindents{paragraph}{10.7em}{5.7em}
\cftsetindents{subparagraph}{12.7em}{6.7em}

%%% need more space for LoF numbers
\cftsetindents{figure}{0em}{3.0em}

%%% and do the same for the LoT
\cftsetindents{table}{0em}{3.0em}

%%% set up the page layout
\settrimmedsize{\stockheight}{\stockwidth}{*}	% Use entire page
\settrims{0pt}{0pt}

\setlrmarginsandblock{1.5in}{1.5in}{*}
\setulmarginsandblock{1.5in}{1.5in}{*}

\setmarginnotes{17pt}{51pt}{\onelineskip}
\setheadfoot{\onelineskip}{2\onelineskip}
\setheaderspaces{*}{2\onelineskip}{*}
\checkandfixthelayout

\usepackage{fancyvrb}			% Allow \verbatim et al. in footnotes
\usepackage{graphicx}			% To include graphics in pdf's (jpg, gif, png, etc)
\usepackage{booktabs}			% Better tables
\usepackage{tabulary}			% Support longer table cells
\usepackage[utf8]{inputenc}		% For UTF-8 support
\usepackage[T1]{fontenc}		% Use T1 font encoding for accented characters
\usepackage{xcolor}				% Allow for color (annotations)

%\geometry{landscape}			% Activate for rotated page geometry

%\usepackage[parfill]{parskip}	% Activate to begin paragraphs with an empty
								% line rather than an indent


\def\myauthor{Author}			% In case these were not included in metadata
\def\mytitle{Title}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\bibliocommand{}

\VerbatimFootnotes
\def\myauthor{Jenee Hughes}
\def\baseheaderlevel{1}
\def\format{complete}
\def\mytitle{ThesisDocumentsMelodyMatcher}


%
%	PDF Stuff
%

%\ifpdf							% Removed for XeLaTeX compatibility
%  \pdfoutput=1					% Removed for XeLaTeX compatibility
  \usepackage[
  	plainpages=false,
  	pdfpagelabels,
  	pdftitle={\mytitle},
  	pagebackref,
  	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}
  \usepackage{memhfixc}
%\fi							% Removed for XeLaTeX compatibility


%
% Title Information
%


\ifx\latexauthor\undefined
\else
	\def\myauthor{\latexauthor}
\fi

\ifx\subtitle\undefined
\else
	\addtodef{\mytitle}{}{ \\ \subtitle}
\fi

\ifx\affiliation\undefined
\else
	\addtodef{\myauthor}{}{ \\ \affiliation}
\fi

\ifx\address\undefined
\else
	\addtodef{\myauthor}{}{ \\ \address}
\fi

\ifx\phone\undefined
\else
	\addtodef{\myauthor}{}{ \\ \phone}
\fi

\ifx\email\undefined
\else
	\addtodef{\myauthor}{}{ \\ \email}
\fi

\ifx\web\undefined
	\else
		\addtodef{\myauthor}{}{ \\ \web}
\fi

\title{\mytitle}
\author{\myauthor}

\begin{document}

\chapterstyle{\mychapterstyle}
\pagestyle{\mypagestyle}

%
%		Front Matter
%

\frontmatter


% Title Page

\maketitle
\clearpage

% Copyright Page
\vspace*{\fill}

\setlength{\parindent}{0pt}

\ifx\mycopyright\undefined
\else
	\textcopyright{} \mycopyright
\fi

\revision

\begin{center}
\framebox{ \parbox[t]{1.5in}{\centering Formatted for \LaTeX  \\ 
 by MultiMarkdown}}
\end{center}

\setlength{\parindent}{1em}
\clearpage

% Table of Contents
\tableofcontents
%\listoffigures			% activate to include a List of Figures
%\listoftables			% activate to include a List of Tables


%
% Main Content
%


% Layout settings
\setlength{\parindent}{1em}

\mainmatter
Full Table of Phone Makeup and Length
SAMPA
Example
Type/
Manner of Articulation
Voiced/ Voiceless
Starts as
Ends as
Cat.
Weight
p
pen, spin, tip
plosive
voiceless
block
block
Con.
8
b
but, web
plosive
voiced
block
block
Con.
7
t
two, sting, bet
plosive
voiceless
block
block
Con.
8
d
do, odd
plosive
voiced
block
block
Con.
7
tS
chair, nature, teach
affricate
voiceless
block
cont fric
Con.
6
dZ
gin, joy, edge
affricate
voiced
block
cont fric
Con.
5
k
cat,kill,queen,thick
plosive
voiceless
block
block
Con.
8
g
go, get, beg
plosive
voiced
block
block
Con.
7
f
fool, enough, leaf
fricative
voiceless
cont fric
cont fric
Con.
4
v
voice, have, of
fricative
voiced
cont fric
cont fric
Con.
3
T
thing, breath
fricative
voiceless
cont fric
cont fric
Con.
4
D
this, breathe
fricative
voiced
cont fric
cont fric
Con.
3
s
see, city, pass
fricative
voiceless
cont fric
cont fric
Con.
4
z
zoo, rose
fricative
voiced
cont fric
cont fric
Con.
3
S
she,sure,emotion,leash
fricative
voiceless
cont fric
cont fric
Con.
4
Z
pleasure, beige
fricative
voiced
cont fric
cont fric
Con.
3
h
ham
fricative
voiceless
cont fric
cont fric
Con.
4
m
man, ham
nasal
voiced
redirect
redirect
Con.
1
n
no, tin
nasal
voiced
redirect
redirect
Con.
1
N
singer, ring
nasal
voiced
redirect
redirect
Con.
1
l
left, bell
lateral
voiced
continuous
continuous
Con.
0
r
run, very
approximant
voiced
continuous
continuous
Con.
0
w
we
semivowel
voiced
continuous
end
Con.
2
j
yes
semivowel
voiced
continuous
end
Con.
2
W
what (Scottish)
approximant
voiceless
continuous
end
Con.
3
x
loch (Scottish)
fricative
voiceless
cont fric
cont fric
Con.
4
A
father, not, law
short


Vow.
0.25
I
city
short


Vow.
0.25
E
bed
short


Vow.
0.25
3\texttt{/}r
bird, winner
short


Vow.
0.25
\{
lad, cat, ran
short


Vow.
0.25
u
soon, through
short


Vow.
0.25
@
about
short


Vow.
0.25
jU/ju
use, pupil
diphthong


semivowel
short
Dip.
0.5
i
see
long


Vow.
0.75
V
run, enough
short


Vow.
0.25
U
put
long


Vow.
0.75
e
day
long


Vow.
0.75
O
or, shore
long


Vow.
0.75
a
DNE in GenAm
long


Vow.
0.75
aI
my, height
diphthong


long
short
Dip.
1
OI
boy
diphthong


long
short
Dip.
1
oU/ou
boat
diphthong


short
long
Dip.
1
aU
now
diphthong


long
long
Dip.


\part{1.5}
\label{}

ridden
semivowel


Vow.
0.25


%
% Back Matter
%

\backmatter
%\appendixpage

%	Bibliography
\bibliographystyle{\mybibliostyle}
\bibliocommand

%	Glossary
\printglossary


%	Index
\printindex

\end{document}
